Inference for trans-dimensional Bayesian models with Diffusive Nested Sampling

### 2014-06-27 Documents/Paper/ms.tex
More writing about proposal

When using DNS,
the proposals typically should be very heavy tailed. When
DNS is exploring a distribution close to the prior, large proposals will
generally be needed to explore the prior efficiently.
When DNS is exploring a distribution constrained to
very high values of the likelihood function, much smaller proposals will be
appropriate. Rather than attempting expensive tuning (since the number of
distributions involved may number in the hundreds or even thousands), we will
apply the heavy tailed proposal distributions and simply accept that there will
be some waste. If a parameter $u$ has a uniform prior between 0 and 1, then
a heavy-tailed proposal is defined by:
\begin{eqnarray}
u' &=& \textnormal{mod}\left(u + 10^{1.5 - 6a}b, 1\right)
\end{eqnarray}
where $a \sim \textnormal{Uniform}(0, 1)$ and $b\sim \mathcal{N}(0,1)$. When
$a$ is close to zero, the size of the proposal is of order 10, which (because
of the mod function) effectively randomises $u'$ from the prior. If $a$ is
close to 1, the scale of the proposal is roughly $10^{-4}$ times the prior
width.

Most of the proposals involve changing one (or a subset) of the parameters
and/or hyperparameters while keeping the others fixed, and are heavy-t

>>>>

When using DNS,
the proposals typically should be very heavy tailed. When
DNS is exploring a distribution close to the prior, large proposals will
generally be needed to explore the prior efficiently.
When DNS is exploring a distribution constrained to
very high values of the likelihood function, much smaller proposals will be
appropriate. Rather than attempting expensive tuning (since the number of
distributions involved may number in the hundreds or even thousands), we will
apply the heavy tailed proposal distributions and simply accept that there will
be some waste. If a parameter $u$ has a uniform prior between 0 and 1, then
a heavy-tailed proposal is defined by:
\begin{eqnarray}
u' &=& \textnormal{mod}\left(u + 10^{1.5 - 6a}b, 1\right)
\end{eqnarray}
where $a \sim \textnormal{Uniform}(0, 1)$ and $b\sim \mathcal{N}(0,1)$.
This is like a standard gaussian/normal random walk proposal, but with a
non-fixed step size, resulting in a scale mixture of normals.
When
$a$ is close to zero, the size of the proposal is of order 10, which (because
of the mod function) effectively randomises $u'$ from the prior. If $a$ is
close to 1, the scale of the proposal is roughly $10^{-4}$ times the prior
width. The coefficient of $a$ was set to 6 because smaller proposals are
usually not necessary. The value 1.5 in the exponent was found to optimize the
performance of this proposal when sampling from $U(0, 1)$ and $\mathcal{N}(0,1)$
priors.

Most of the proposals involve changing one (or a subset) of the parameters
and/or hyperparameters while keeping the others fixed.
